---
title: "America's ex-top 100 golf courses"
#author: "Compiled by Skip Perry, October 2020"
output: html_document
---

```{r setup, include=FALSE}
options(dplyr.summarise.inform = F)
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library(lubridate)
library(gridExtra)
#library(DT)
source("/Users/skipperry/Documents/golf_course_rankings/plot_rankings.R")
source("/Users/skipperry/Documents/golf_course_rankings/course_categories.R")
```

*** 

Unlike country club memberships, golf courses don't always get to keep their spots in the Top 100 for life. The following `r ex_top_100_df %>% count()` courses used to be ranked in one of the two Top 100 lists but have dropped off. They have been sorted by the number of times they appeared on a list, with ties broken by their best rank achieved.

As of 2015 there were about 16,000 golf courses in the USA, `r current_top_100_df %>% bind_rows(ex_top_100_df) %>% count()` of which have been ranked in the Top 100 at some point. Making even a single appearance is something to be proud of. 

***

```{r}
df <- 
  all_rankings %>% 
  inner_join(ex_top_100_df, by = "Course") %>% 
  group_by(Course) %>% 
  mutate(
    max_year = max(Year),
    times_ranked = n(),
    min_rank_overall = min(Ranking)
  ) %>% 
  group_by(Course, Publication, max_year, times_ranked, min_rank_overall) %>% 
  summarize(Ranking = min(Ranking)) %>% 
  ungroup() %>% 
  spread(Publication, Ranking) %>% 
  mutate_at(vars(`Golf Digest`, `Golf Magazine`), ~ if_else(is.na(.), '-', as.character(.))) %>% 
  inner_join(
    course_info %>% 
      transmute(Course, Location = str_c(City, ", ", State), Year_Designed), 
    by = "Course"
  ) %>% 
  transmute(
    Course, Location, `Year Designed` = Year_Designed, 
    `Number of Appearances` = times_ranked, `Last Year Ranked` = max_year,
    `Best Golf Digest Ranking` = `Golf Digest`,
    `Best Golf Magazine Ranking` = `Golf Magazine`,
    min_rank_overall
  ) %>% 
  arrange(desc(`Number of Appearances`), min_rank_overall, desc(`Last Year Ranked`)) %>% 
  select(-min_rank_overall)

base_url <- "https://top100golf.github.io/"
base_url_rep <- rep(base_url, nrow(df))

df %>% 
  mutate(Course = str_c("[", Course, "](", base_url, str_replace_all(Course, "\\(|\\)|\\s|\\'", "-"), ".html)")) %>% 
  knitr::kable(align = "c")
```
