```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library(lubridate)
library(gridExtra)
library(geosphere)
source("/Users/skipperry/Documents/golf_course_rankings/plot_rankings.R")
source("/Users/skipperry/Documents/golf_course_rankings/course_categories.R")
```

---
title: America's top 100 golf courses
---

***

```{r}
last_two_rankings <- 
  tribble(
    ~Publication, ~Year,
    "Golf Digest", 2019,
    "Golf Digest", 2021,
    "Golf Magazine", 2017,
    "Golf Magazine", 2019
  ) %>% 
  mutate(Order = c(1, 2, 1, 2))
```

```{r}
changes <- 
  all_rankings %>% 
  inner_join(last_two_rankings, by = c("Publication", "Year")) %>% 
  select(Ranking, Course, Publication, Year, Order) %>% 
  mutate(Year = if_else(Order == 2, "Current", "Previous")) %>% 
  select(-Order) %>% 
  spread(Year, Ranking) %>% 
  mutate(
    chg = Previous - Current,
    chg_na = case_when(
      is.na(Previous) ~ 101 - Current,
      is.na(Current) ~ Previous - 101,
      TRUE ~ Previous - Current
    )
  )

new_courses <- 
  changes %>% 
  filter(is.na(Previous)) %>% 
  mutate(Ranking = Current) %>% 
  arrange(Ranking)

gone_courses <- 
  changes %>% 
  filter(is.na(Current)) %>% 
  mutate(Ranking = Previous) %>% 
  arrange(Ranking)

course_list_to_text <- function(df, publication) {
  df %>% 
    filter(Publication == publication) %>% 
    mutate(
      Ranking_Label = case_when(
        Ranking %% 10 == 1 ~ str_c(Ranking, "st"),
        Ranking %% 10 == 2 ~ str_c(Ranking, "nd"),
        Ranking %% 10 == 3 ~ str_c(Ranking, "rd"),
        Ranking %% 10 %in% c(0, 4:9) ~ str_c(Ranking, "th"),
        TRUE ~ NA_character_
      ),
      Course_Rank = str_c(Course, " (", Ranking_Label, ")")
    ) %>% 
    pull(Course_Rank) %>% 
    paste0(collapse = ", ")
}

new_golf_digest <-
  course_list_to_text(df = new_courses, publication = "Golf Digest")

new_golf_mag <-
  course_list_to_text(df = new_courses, publication = "Golf Magazine")

gone_golf_digest <-
  course_list_to_text(df = gone_courses, publication = "Golf Digest")

gone_golf_mag <-
  course_list_to_text(df = gone_courses, publication = "Golf Magazine")

biggest_drops <-
  changes %>% 
  group_by(Publication) %>% 
  arrange(chg_na) %>% 
  mutate(
    Current_Label = case_when(
      Current %% 10 == 1 ~ str_c(Current, "st"),
      Current %% 10 == 2 ~ str_c(Current, "nd"),
      Current %% 10 == 3 ~ str_c(Current, "rd"),
      Current %% 10 %in% c(0, 4:9) ~ str_c(Current, "th"),
      TRUE ~ NA_character_
    ),
    Previous_Label = case_when(
      Previous %% 10 == 1 ~ str_c(Previous, "st"),
      Previous %% 10 == 2 ~ str_c(Previous, "nd"),
      Previous %% 10 == 3 ~ str_c(Previous, "rd"),
      Previous %% 10 %in% c(0, 4:9) ~ str_c(Previous, "th"),
      TRUE ~ NA_character_
    ),
    chg_na = -1 * chg_na, 
    Current_Text = if_else(is.na(Current), "unranked", as.character(Current_Label)),
    chg_na_text = if_else(is.na(Current), str_c(chg_na, "+"), as.character(chg_na))
  ) %>% 
  transmute(value = str_c(Course, ": ", chg_na_text, " spots, ", Previous_Label, " to ", Current_Text))

biggest_rises <-
  changes %>% 
  left_join(course_info %>% select(Course, Year_Designed), by = "Course") %>% 
  #### NOTE HARDCODED 2019
  filter(Year_Designed < 2019) %>% 
  #### NOTE HARDCODED 2019
  group_by(Publication) %>% 
  arrange(desc(chg_na)) %>% 
  mutate(
    Current_Label = case_when(
      Current %% 10 == 1 ~ str_c(Current, "st"),
      Current %% 10 == 2 ~ str_c(Current, "nd"),
      Current %% 10 == 3 ~ str_c(Current, "rd"),
      Current %% 10 %in% c(0, 4:9) ~ str_c(Current, "th"),
      TRUE ~ NA_character_
    ),
    Previous_Label = case_when(
      Previous %% 10 == 1 ~ str_c(Previous, "st"),
      Previous %% 10 == 2 ~ str_c(Previous, "nd"),
      Previous %% 10 == 3 ~ str_c(Previous, "rd"),
      Previous %% 10 %in% c(0, 4:9) ~ str_c(Previous, "th"),
      TRUE ~ NA_character_
    ),
    Previous_Text = if_else(is.na(Previous), "unranked", as.character(Previous_Label)),
    chg_na_text = if_else(is.na(Previous), str_c(chg_na, "+"), as.character(chg_na))
  ) %>% 
  transmute(value = str_c(Course, ": ", chg_na_text, " spots, ", Previous_Text, " to ", Current_Label))
```

### Summary of changes from previous rankings

<u>New entries</u>

* Golf Digest
  * `r new_golf_digest`
* Golf Magazine
  * `r new_golf_mag`
  
<u>Fell off the ranking</u>

* Golf Digest
  * `r gone_golf_digest`
* Golf Magazine
  * `r gone_golf_mag`

<u>Biggest improvements</u>

  * Golf Digest
    * `r biggest_rises %>% filter(Publication == "Golf Digest") %>% slice(1) %>% pull(value)`
    * `r biggest_rises %>% filter(Publication == "Golf Digest") %>% slice(2) %>% pull(value)`
    * `r biggest_rises %>% filter(Publication == "Golf Digest") %>% slice(3) %>% pull(value)`
    * `r biggest_rises %>% filter(Publication == "Golf Digest") %>% slice(4) %>% pull(value)`
    * `r biggest_rises %>% filter(Publication == "Golf Digest") %>% slice(5) %>% pull(value)`
  * Golf Magazine
    * `r biggest_rises %>% filter(Publication == "Golf Magazine") %>% slice(1) %>% pull(value)`
    * `r biggest_rises %>% filter(Publication == "Golf Magazine") %>% slice(2) %>% pull(value)`
    * `r biggest_rises %>% filter(Publication == "Golf Magazine") %>% slice(3) %>% pull(value)`
    * `r biggest_rises %>% filter(Publication == "Golf Magazine") %>% slice(4) %>% pull(value)`
    * `r biggest_rises %>% filter(Publication == "Golf Magazine") %>% slice(5) %>% pull(value)`

<u>Biggest drops</u>

  * Golf Digest
    * `r biggest_drops %>% filter(Publication == "Golf Digest") %>% slice(1) %>% pull(value)`
    * `r biggest_drops %>% filter(Publication == "Golf Digest") %>% slice(2) %>% pull(value)`
    * `r biggest_drops %>% filter(Publication == "Golf Digest") %>% slice(3) %>% pull(value)`
    * `r biggest_drops %>% filter(Publication == "Golf Digest") %>% slice(4) %>% pull(value)`
    * `r biggest_drops %>% filter(Publication == "Golf Digest") %>% slice(5) %>% pull(value)`
  * Golf Magazine
    * `r biggest_drops %>% filter(Publication == "Golf Magazine") %>% slice(1) %>% pull(value)`
    * `r biggest_drops %>% filter(Publication == "Golf Magazine") %>% slice(2) %>% pull(value)`
    * `r biggest_drops %>% filter(Publication == "Golf Magazine") %>% slice(3) %>% pull(value)`
    * `r biggest_drops %>% filter(Publication == "Golf Magazine") %>% slice(4) %>% pull(value)`
    * `r biggest_drops %>% filter(Publication == "Golf Magazine") %>% slice(5) %>% pull(value)`
    
***

## Latest rankings 

```{r, echo=FALSE}
df <- 
  all_rankings %>% 
  inner_join(last_two_rankings, by = c("Publication", "Year")) %>% 
  filter(Order == 2) %>% 
  select(Ranking, Course, Publication) %>% 
  spread(Publication, Ranking) %>% 
  mutate(Average = (`Golf Digest` + `Golf Magazine`) / 2) %>% 
  inner_join(course_info, by = "Course") %>% 
  transmute(
    Course, Location = str_c(City, ", ", State), 
    `Designer(s)` = case_when(
      is.na(Designer2) ~ Designer1,
      is.na(Designer3) ~ str_c(Designer1, Designer2, sep = ", "),
      TRUE ~ str_c(Designer1, Designer2, Designer3, sep = ", ")
    ),
    `Year Designed` = Year_Designed, `Golf Digest`, `Golf Magazine`, Average,
    Top_Rating = case_when(
      is.na(`Golf Digest`) | `Golf Digest` > `Golf Magazine` ~ `Golf Magazine`,
      TRUE ~ `Golf Digest`
    )
  ) %>% 
  arrange(Average, Top_Rating) %>% 
  select(-Top_Rating) %>% 
  mutate_at(
    vars(`Golf Digest`, `Golf Magazine`, `Average`), 
    ~ if_else(is.na(.), '-', as.character(.))
  ) %>% 
  rename(`Golf Digest 2021` = `Golf Digest`, `Golf Magazine 2019` = `Golf Magazine`)

base_url <- "https://top100golf.github.io/"
base_url_rep <- rep(base_url, nrow(df))

df %>% 
  select(-`Designer(s)`) %>% 
  mutate(Course = str_c("[", Course, "](", base_url, str_replace_all(Course, "\\(|\\)|\\s|\\'", "-"), ".html)")) %>% 
  knitr::kable(align = "c")
```
